### 2023-05-03 README.Rmd
Updates to docs to reference Rainey (2023)

The plot of the simulated sampling distribution indicates that the sampling distribution for the risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.

@@

>>>>

# Plot the resulting sampling distributions
plot(sim_est, reference = TRUE, ci = FALSE)
```

The plot of the simulated sampling distribution indicates that the sampling distribution for the risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid. Note that the estimates are those computed from the original model coefficients; the distribution is used only for computing confidence intervals, in line with recommendations by Rainey (2023).

@@

Rainey, C. (2023). A careful consideration of CLARIFY: Simulation-induced bias in point estimates of quantities of interest. *Political Science Research and Methods*, 1–10. https://doi.org/10.1017/psrm.2023.8
